---
title: "California Billionaires: Wealth, Taxes, and Wealth Tax Revenue Estimates"
subtitle: "R replication of Boll, Saez, and Zucman (2026) — NBER WP 35218"
author: "Fernando Hoces de la Guardia"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    documentclass: article
    fontsize: 11pt
    geometry: margin=1in
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(targets)
library(gt)
library(ggplot2)
```

## Overview

This document is a section-by-section R replication of *California Billionaires:
Wealth, Taxes, and Wealth Tax Revenue Estimates* by Jasper Boll, Emmanuel Saez,
and Gabriel Zucman (NBER Working Paper No. 35218, May 2026). Every table and
figure embedded below is built from the project's `{targets}` pipeline; the
upstream targets re-derive each Excel cell of the BSZ supplementary workbook in
R and verify element-wise against the cached values (see `Phase 2` in
`memory/project_state.md`).

The text from the original paper is shown in **blockquotes**; section commentary
outside the blockquotes is the replicator's own.

### Abstract (verbatim from BSZ 2026)

> This paper documents the wealth of California's billionaires and the taxes
> they pay. California billionaires' wealth exceeds \$2 trillion today, the
> equivalent of 50% of California's GDP. It has grown 144% from 2023 to 2025,
> fueled by the AI boom. Over the longer run, the real wealth of California's
> billionaire class — the 0.0002% richest households — has been multiplied by
> 30 from 1982 to 2025, while average real family income in California has
> about doubled. California billionaires pay about 0.2% of their wealth in
> California income tax (\$3.2 billion/year), representing 2.4% of total
> California income tax revenue on average over 2023-2025. Using Securities
> and Exchange Commission data from Alphabet, Meta, Oracle, and Nvidia since
> 2004, we estimate the trajectory of wealth, income, and taxes paid by the
> top 4 California billionaires — Page, Brin, Zuckerberg, Ellison (through
> 2020), and Huang (since 2021) — focusing on their business wealth. This
> group alone holds nearly \$1 trillion in business wealth, almost half of
> total California billionaire wealth. For this group, wealth growth (+322%
> over 2023-2025) and low taxation (0.04% of wealth in annual California
> income tax) are more pronounced. The proposed one-off California billionaire
> tax of 5%, payable over 5 years, is both small relative to California
> billionaires' wealth gains and large relative to the taxes they currently
> pay. We estimate that it could raise about \$100 billion, with comparatively
> minor impacts on income tax revenue. Using empirical estimates of mobility
> responses to wealth taxation, we find that an annual wealth tax on
> California billionaires could raise substantial additional revenue even
> after accounting for income tax losses due to mobility.

# 1. California Billionaires Wealth Growth

This section documents the level and growth of California billionaire wealth,
both recent (2019-2025, where SEC Form 4 filings give per-individual detail)
and long-run (1982-2025, where Forbes 400 lists give the top .0002%).

## 1.1 Recent and long-term wealth growth

Table 1 (Panel A) shows nominal wealth for the four most recent years and the
cumulative growth from 2023 to 2025. Panel B compares 1982 vs. 2025 in real
2025 dollars for the top .0002% wealthiest California families.

```{r tab1}
tar_read(tab1_gt)
```

Figure 1 visualizes the same growth episode for both all California
billionaires and the top 4 (Page, Brin, Zuckerberg, Huang), with dashed
segments illustrating the impact of a hypothetical 5% wealth tax on 2025
year-end wealth.

```{r fig1, fig.width=7, fig.height=5}
tar_read(fig1)
```

Figure 2 places this in the long run. Panel A juxtaposes the real wealth of
the top .0002% California families against California GDP per family
(1982-2025, both in 2025 dollars). Panel B expresses the top .0002% wealth
as a share of GDP for both the US (top 400 families) and California (top 45
families).

```{r fig2, fig.width=11, fig.height=5}
tar_read(fig2)
```

# 2. Taxes paid by California Billionaires

Section 2 estimates the California income tax paid by California billionaires
each year from 2019 through 2025. Two complementary approaches are used: a
top-down extrapolation from California Franchise Tax Board (FTB) tabulated
statistics for high-AGI brackets, and a bottom-up calculation from SEC Form 4
filings of the top-4 holders' realized capital gains, dividends, and exercised
stock options.

## 2.1 Headline estimates for all California billionaires

```{r tab2}
tar_read(tab2_gt)
```

```{r fig3, fig.width=11, fig.height=5}
tar_read(fig3)
```

## 2.2 Per-billionaire detail (Top 4)

```{r tab3}
tar_read(tab3_gt)
```

```{r tab4}
tar_read(tab4_gt)
```

## 2.3 Total tax burden relative to wealth

Figure 4 stacks the four tax components (California income tax, federal income
tax, corporate taxes, property + sales taxes) as a fraction of total wealth
for all California billionaires, 2019-2025.

```{r fig4, fig.width=7, fig.height=5}
tar_read(fig4)
```

Figure 5 compares the cumulative size of three income/wealth concepts for the
Top 4 (Fiscal Income, Economic Income, Wealth Gain) and decomposes each into
net-of-taxes plus tax components.

```{r fig5, fig.width=7, fig.height=5}
tar_read(fig5)
```

Figure 6 traces the Top 4's effective tax rate on wealth and on economic
income across the 2004-2025 panel, and Figure 7 places those rates next to
the US-wide and California-wide averages from the Distributional National
Accounts (Saez and Zucman).

```{r fig6, fig.width=11, fig.height=5}
tar_read(fig6)
```

```{r fig7, fig.width=11, fig.height=5}
tar_read(fig7)
```

# 3. The Economics of Taxing California Billionaires' Wealth

Section 3 scores two policy options: a one-time 5% wealth tax payable over
five years, and a permanent annual wealth tax.

## 3.1 One-time wealth tax

Table 5 reports four scenarios for the one-time tax. The benchmark uses the
Forbes 4/15/2026 billionaire list and a 10% avoidance rate. Scenarios 2-4
add Pareto-extrapolated missing small billionaires and an aggressive
pre/post-2026-leaver assumption.

```{r tab5}
tar_read(tab5_gt)
```

## 3.2 Permanent Billionaire Wealth Tax

Figure 8 plots the Laffer curve for a permanent annual California wealth tax
under three behavioral scenarios: mechanical (no response), short-run
(mobility semi-elasticity *e* = 10), and long-run (mobility plus
deconcentration elasticity *d* = 15).

```{r fig8, fig.width=7, fig.height=5}
tar_read(fig8)
```

# Appendix

## A.1 US wealth growth comparison

Table A1 mirrors Table 1 for the US rather than California.

```{r tab_a1}
tar_read(tab_a1_gt)
```

## A.2 Industry composition

```{r fig_a1, fig.width=8, fig.height=6}
tar_read(fig_a1)
```

## A.3 Robustness: alternative method for CA income tax

```{r fig_a2, fig.width=7, fig.height=5}
tar_read(fig_a2)
```

## A.4 Taxes on public-stock wealth

```{r fig_a3, fig.width=11, fig.height=5}
tar_read(fig_a3)
```

## A.5 Pareto extrapolation for missing billionaires

```{r fig_a4, fig.width=11, fig.height=5}
tar_read(fig_a4)
```

# Reproducibility

This report is built from the `{targets}` pipeline rooted at
`~/Desktop/sandbox/CAWT-BSZ`. All upstream inputs come from
`original-materials/BSZ_MainTablesFigures.xlsx`. To re-render:

```r
targets::tar_make()
quarto::quarto_render("report.qmd")
```

The 473-expectation `testthat` suite (`Rscript tests/testthat.R`) verifies
every Phase-2 R re-derivation against the Excel cached values within
documented tolerances.
