---
title: "Reproduction of: California Billionaires: Wealth, Taxes, and Wealth Tax Revenue Estimates"
subtitle: "R replication of Boll, Saez, and Zucman (2026) — NBER WP 35218"
author: "Fernando Hoces de la Guardia"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    documentclass: article
    fontsize: 11pt
    geometry: margin=1in
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(targets)
library(gt)
library(ggplot2)
# Source R/ files. keep.source = TRUE preserves srcref attributes so the
# read-only code listings below can pull each function body straight from
# disk and report its exact file:line range.
options(keep.source = TRUE)
invisible(lapply(list.files("R", pattern = "\\.R$", full.names = TRUE), source))
```

## Overview

This document is a section-by-section R replication of *California Billionaires:
Wealth, Taxes, and Wealth Tax Revenue Estimates* by Jasper Boll, Emmanuel Saez,
and Gabriel Zucman (NBER Working Paper No. 35218, May 2026). Every table and
figure embedded below is built from the project's `{targets}` pipeline; the
upstream targets re-derive each Excel cell of the BSZ supplementary workbook in
R and verify element-wise against the cached values; see the project README
for the full pipeline structure.

The text from the original paper is shown in **blockquotes**; section commentary
outside the blockquotes is the replicator's own.

### Abstract (verbatim from BSZ 2026)

> This paper documents the wealth of California's billionaires and the taxes
> they pay. California billionaires' wealth exceeds \$2 trillion today, the
> equivalent of 50% of California's GDP. It has grown 144% from 2023 to 2025,
> fueled by the AI boom. Over the longer run, the real wealth of California's
> billionaire class — the 0.0002% richest households — has been multiplied by
> 30 from 1982 to 2025, while average real family income in California has
> about doubled. California billionaires pay about 0.2% of their wealth in
> California income tax (\$3.2 billion/year), representing 2.4% of total
> California income tax revenue on average over 2023-2025. Using Securities
> and Exchange Commission data from Alphabet, Meta, Oracle, and Nvidia since
> 2004, we estimate the trajectory of wealth, income, and taxes paid by the
> top 4 California billionaires — Page, Brin, Zuckerberg, Ellison (through
> 2020), and Huang (since 2021) — focusing on their business wealth. This
> group alone holds nearly \$1 trillion in business wealth, almost half of
> total California billionaire wealth. For this group, wealth growth (+322%
> over 2023-2025) and low taxation (0.04% of wealth in annual California
> income tax) are more pronounced. The proposed one-off California billionaire
> tax of 5%, payable over 5 years, is both small relative to California
> billionaires' wealth gains and large relative to the taxes they currently
> pay. We estimate that it could raise about \$100 billion, with comparatively
> minor impacts on income tax revenue. Using empirical estimates of mobility
> responses to wealth taxation, we find that an annual wealth tax on
> California billionaires could raise substantial additional revenue even
> after accounting for income tax losses due to mobility.


## R re-derivations (computed once, cached, reused below)

```{r compute-outputs, eval=FALSE, echo=TRUE}
data_sec_agg_r           <- compute_data_sec_agg(data_sec_all)
pareto_missing_r         <- compute_pareto_missing(pareto_missing)
pareto_summary           <- compute_pareto_summary(pareto_missing_r)
tab5_r                   <- compute_tab5(pareto_missing_r, tab2, tab3)
fig8_laffer_r            <- compute_fig8_laffer()
billionaires_ca_inctax_r <- compute_billionaires_ca_inctax(
                              data_sec_agg_r, billionaires_ca_inctax, ftb_b4a)
shortrunseries_r         <- compute_shortrunseries(
                              data_sec_agg_r, data_sec_top4,
                              billionaires_ca_inctax_r, shortrunseries)
top4taxes_r              <- compute_top4taxes(data_sec_top4)
# Read-only display. Function bodies live in R/compute_*.R; tar_target() wiring
# is in _targets.R. The report imports each value via tar_read(<name>).
```

# 1. California Billionaires Wealth Growth

This section documents the level and growth of California billionaire wealth,
both recent (2019-2025, where SEC Form 4 filings give per-individual detail)
and long-run (1982-2025, where Forbes 400 lists give the top .0002%).

## 1.1 Recent and long-term wealth growth

> Table 1 Panel A provides basic statistics on California billionaires in
> recent years. Appendix Table A1 provides the same statistics at the US level
> (instead of California). \[…\] Larry Ellison is excluded from these series
> throughout the 2019 to 2025 period for consistency. (BSZ 2026, p. 3)

**How it is built.** Table 1 is rendered by
[`build_tab1()`](#sec-build_tab1) from three upstream tibbles —
[`compute_data_sec_agg()`](#sec-compute_data_sec_agg) for the year-by-year
totals, [`compute_shortrunseries()`](#sec-compute_shortrunseries) for the
top-4 wealth column, and [`extract_longrunseries()`](#sec-extract_longrunseries)
for CA GDP. Each function name links to its source in the Source code
appendix.

```{r tab1-call, eval=FALSE, echo=TRUE}
data_sec_agg_r   <- compute_data_sec_agg(data_sec_all)
shortrunseries_r <- compute_shortrunseries(
                       data_sec_agg_r, data_sec_top4,
                       billionaires_ca_inctax_r, shortrunseries)
build_tab1(data_sec_agg_r, shortrunseries_r, longrunseries)
# Read-only display. _targets.R wires these into the pipeline.
```

```{r tab1}
tar_read(tab1_gt)
```

> Figure 1 plots the trajectory of California's billionaires' total wealth
> (in nominal current dollars) at the end of years 2019 to 2025, the longest
> time series we have for all California billionaires. It also plots the
> wealth trajectory of the top 4 (Larry Page, Sergei Brin, Mark Zuckerberg,
> and Jensen Huang) who are centi-billionaires (wealth above \$100 billion).
> (BSZ 2026, p. 2–3)

**How it is built.** Figure 1 is rendered by [`build_fig1()`](#sec-build_fig1)
from a single tibble produced by [`compute_shortrunseries()`](#sec-compute_shortrunseries).

```{r fig1-call, eval=FALSE, echo=TRUE}
build_fig1(shortrunseries_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig1, fig.width=7, fig.height=5}
tar_read(fig1)
```

> Figure 2 depicts the full time series. Panel A depicts the trajectory of
> top .0002% wealth (top 45 families in California today) in 2025 \$ billions
> vs. the trajectory of California GDP per family. (BSZ 2026, p. 4)

**How it is built.** Figure 2 is rendered by [`build_fig2()`](#sec-build_fig2)
from the positional dump produced by
[`extract_longrunseries()`](#sec-extract_longrunseries).

```{r fig2-call, eval=FALSE, echo=TRUE}
build_fig2(longrunseries)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig2, fig.width=11, fig.height=5}
tar_read(fig2)
```

# 2. Taxes paid by California Billionaires

Section 2 estimates the California income tax paid by California billionaires
each year from 2019 through 2025. Two complementary approaches are used: a
top-down extrapolation from California Franchise Tax Board (FTB) tabulated
statistics for high-AGI brackets, and a bottom-up calculation from SEC Form 4
filings of the top-4 holders' realized capital gains, dividends, and exercised
stock options.

## 2.1 Headline estimates for all California billionaires

> For all California billionaires, we estimate the California income tax they
> pay using Franchise Tax Board (the California tax administration) tabulated
> statistics, a Pareto extrapolation, and an adjustment based on Federal tax
> data. (BSZ 2026, p. 6)

**How it is built.** Table 2 is rendered by
[`build_tab2()`](#sec-build_tab2) from the year-aggregate
[`compute_data_sec_agg()`](#sec-compute_data_sec_agg), the headline
[`compute_billionaires_ca_inctax()`](#sec-compute_billionaires_ca_inctax),
and the per-billionaire panel from
[`extract_data_sec_top4()`](#sec-extract_data_sec_top4).

```{r tab2-call, eval=FALSE, echo=TRUE}
build_tab2(data_sec_agg_r, billionaires_ca_inctax_r, data_sec_top4)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r tab2}
tar_read(tab2_gt)
```

> Figure 3 depicts the estimated annual California individual income tax
> paid by all California billionaires and the top 4 (in nominal \$ billions)
> each year from 2019 to 2025. (BSZ 2026, p. 7)

**How it is built.** Figure 3 is rendered by
[`build_fig3()`](#sec-build_fig3) from
[`compute_shortrunseries()`](#sec-compute_shortrunseries).

```{r fig3-call, eval=FALSE, echo=TRUE}
build_fig3(shortrunseries_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig3, fig.width=11, fig.height=5}
tar_read(fig3)
```

## 2.2 Per-billionaire detail (Top 4)

> Table 3 reports statistics for each of the top 4. (BSZ 2026, p. 7)

**How it is built.** Table 3 is rendered by
[`build_tab3()`](#sec-build_tab3) from
[`extract_data_sec_top4()`](#sec-extract_data_sec_top4).

```{r tab3-call, eval=FALSE, echo=TRUE}
build_tab3(data_sec_top4)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r tab3}
tar_read(tab3_gt)
```

> Table 4. First, their companies pay low dividends relative to the
> corporate net profits they make. \[…\] Second, they realize modest capital
> gains relative to the enormous wealth gains they are making. (BSZ 2026, p. 10)

**How it is built.** Table 4 is rendered by
[`build_tab4()`](#sec-build_tab4) from
[`extract_data_sec_top4()`](#sec-extract_data_sec_top4).

```{r tab4-call, eval=FALSE, echo=TRUE}
build_tab4(data_sec_top4)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r tab4}
tar_read(tab4_gt)
```

## 2.3 Total tax burden relative to wealth

> Figure 4 depicts the estimated total annual taxes paid by all California
> billionaires and the composition by tax type from 2019 to 2025 relative
> to end of year wealth. Federal and California individual income taxes are
> estimated using Franchise Tax Board tabulated statistics, a simple Pareto
> extrapolation, and an adjustment based on Federal tax data. (BSZ 2026, p. 8)

**How it is built.** Figure 4 is rendered by
[`build_fig4()`](#sec-build_fig4) from the `all_taxes` block of
[`compute_billionaires_ca_inctax()`](#sec-compute_billionaires_ca_inctax).

```{r fig4-call, eval=FALSE, echo=TRUE}
build_fig4(billionaires_ca_inctax_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig4, fig.width=7, fig.height=5}
tar_read(fig4)
```

> Figure 5 illustrates the statistics from Table 4 on income and taxes of
> the top 4 richest Californians in the period 2019-2025 on their company
> wealth (which is 97% of their total wealth at the end of 2025).
> (BSZ 2026, p. 11)

**How it is built.** Figure 5 is rendered by
[`build_fig5()`](#sec-build_fig5) from
[`extract_data_sec_top4()`](#sec-extract_data_sec_top4).

```{r fig5-call, eval=FALSE, echo=TRUE}
build_fig5(data_sec_top4)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig5, fig.width=7, fig.height=5}
tar_read(fig5)
```

> Figure 6 depicts the estimated taxes paid by the top 4 each year from 2004
> to 2025 relative to their wealth (top panel) and relative to their full
> economic income (bottom panel). (BSZ 2026, p. 13)

**How it is built.** Figure 6 is rendered by
[`build_fig6()`](#sec-build_fig6) from the 22-year panel of
[`compute_top4taxes()`](#sec-compute_top4taxes).

```{r fig6-call, eval=FALSE, echo=TRUE}
build_fig6(top4taxes_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig6, fig.width=11, fig.height=5}
tar_read(fig6)
```

> Figure 7 compares taxes paid relative to economic income for the top 4 vs.
> the average economy wide. \[…\] The macroeconomic average effective tax
> rate for the US population is computed using the updated Distributional
> National Accounts series. (BSZ 2026, p. 15)

**How it is built.** Figure 7 is rendered by
[`build_fig7()`](#sec-build_fig7) from
[`compute_top4taxes()`](#sec-compute_top4taxes) and the DINA tables loaded
by [`extract_data_dina()`](#sec-extract_data_dina).

```{r fig7-call, eval=FALSE, echo=TRUE}
build_fig7(top4taxes_r, data_dina)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig7, fig.width=11, fig.height=5}
tar_read(fig7)
```

# 3. The Economics of Taxing California Billionaires' Wealth

Section 3 scores two policy options: a one-time 5% wealth tax payable over
five years, and a permanent annual wealth tax.

## 3.1 One-time wealth tax

> Table 5 reports a column of this extra CA income tax generated assuming
> that wealth taxes will be paid one-third by selling assets triggering
> taxable realized capital gains (with a basis of 20% of selling price
> consistent with our earlier estimation that California billionaire wealth
> is 80% unrealized gains) and two-thirds with liquidities or debt.
> (BSZ 2026, p. 22)

**How it is built.** Table 5 is rendered by
[`build_tab5()`](#sec-build_tab5) from the scoring tibble produced by
[`compute_tab5()`](#sec-compute_tab5), which in turn pulls Pareto
summary stats from [`compute_pareto_missing()`](#sec-compute_pareto_missing)
plus the averages rows of [`extract_tab2()`](#sec-extract_tab2) and
[`extract_tab3()`](#sec-extract_tab3).

```{r tab5-call, eval=FALSE, echo=TRUE}
tab5_r <- compute_tab5(pareto_missing_r, tab2, tab3)
build_tab5(tab5_r)
# Read-only display. _targets.R wires these into the pipeline.
```

```{r tab5}
tar_read(tab5_gt)
```

## 3.2 Permanent Billionaire Wealth Tax

> Figure 8 depicts the revenue collected from billionaires from a permanent
> annual wealth tax as a function of the tax rate (on the x-axis) in the
> solid red line. This tax revenue estimate takes into account income and
> wealth tax revenue lost because of mobility responses calibrated using
> the empirical literature. (BSZ 2026, p. 25)

**How it is built.** Figure 8 is rendered by
[`build_fig8()`](#sec-build_fig8) from the 201-rate Laffer sweep produced
by [`compute_fig8_laffer()`](#sec-compute_fig8_laffer).

```{r fig8-call, eval=FALSE, echo=TRUE}
build_fig8(fig8_laffer_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig8, fig.width=7, fig.height=5}
tar_read(fig8)
```

# Appendix

## A.1 US wealth growth comparison

> Table A1 provides the same statistics at the US level (instead of
> California). (BSZ 2026, p. 3)

**How it is built.** Table A1 is rendered by
[`build_tab_a1()`](#sec-build_tab_a1) from the positional dumps
[`extract_shortrunseries()`](#sec-extract_shortrunseries) (Panel A's #
US-citizen-billionaire count and total wealth) and
[`extract_longrunseries()`](#sec-extract_longrunseries) (Panel B's 1982 vs
2025 long-run real growth).

```{r tab_a1-call, eval=FALSE, echo=TRUE}
build_tab_a1(shortrunseries, longrunseries)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r tab_a1}
tar_read(tab_a1_gt)
```

## A.2 Industry composition

> Figure A1 depicts the industry composition of California billionaires'
> wealth with a breakdown between SEC reported publicly traded stock vs.
> other for each industry. (BSZ 2026, p. 5)

**How it is built.** Figure A1 is rendered by
[`build_fig_a1()`](#sec-build_fig_a1). It reads block 2 of the
`rtb_2026_industry` sheet directly (cols A, G, H, I, rows 22-34) at build
time rather than from a pre-extracted target.

```{r fig_a1-call, eval=FALSE, echo=TRUE}
build_fig_a1(xlsx_path)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig_a1, fig.width=8, fig.height=6}
tar_read(fig_a1)
```

## A.3 Robustness: alternative method for CA income tax

> Appendix Figure A2 displays the California income tax paid by California
> billionaires as a percent of California wide state individual income tax
> revenue. (BSZ 2026, p. 7)

**How it is built.** Figure A2 is rendered by
[`build_fig_a2()`](#sec-build_fig_a2) from
[`compute_shortrunseries()`](#sec-compute_shortrunseries) (the AA / AF
columns express the headline and SEC-top-5 figures as a share of total CA
income tax revenue).

```{r fig_a2-call, eval=FALSE, echo=TRUE}
build_fig_a2(shortrunseries_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig_a2, fig.width=7, fig.height=5}
tar_read(fig_a2)
```

## A.4 Taxes on public-stock wealth

> Figure A3-A produces the same statistics for wealth arising from publicly
> traded stock. (BSZ 2026, p. 36)

**How it is built.** Figure A3 is rendered by
[`build_fig_a3()`](#sec-build_fig_a3) from the `all_taxes` block of
[`compute_billionaires_ca_inctax()`](#sec-compute_billionaires_ca_inctax),
restricting to the public-asset rows (rows 117-135 of the source sheet).

```{r fig_a3-call, eval=FALSE, echo=TRUE}
build_fig_a3(billionaires_ca_inctax_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig_a3, fig.width=11, fig.height=5}
tar_read(fig_a3)
```

## A.5 Pareto extrapolation for missing billionaires

Panel A plots the Pareto coefficient *b* at each wealth threshold (Forbes
data + projected). Panel B compares the density of billionaires-per-bracket
empirically vs. the Pareto-extrapolation that adds the small billionaires
Forbes is likely missing below the \$4.5B anchor.

**How it is built.** Figure A4 is rendered by
[`build_fig_a4()`](#sec-build_fig_a4) from
[`compute_pareto_missing()`](#sec-compute_pareto_missing).

```{r fig_a4-call, eval=FALSE, echo=TRUE}
build_fig_a4(pareto_missing_r)
# Read-only display. _targets.R wires this into the pipeline.
```

```{r fig_a4, fig.width=11, fig.height=5}
tar_read(fig_a4)
```

# Source code {#sec-source-code}

The function bodies listed below live in `R/*.R` files (one canonical
location per function). Each listing is pulled from disk at render time via
R's `getSrcref()` so the report never drifts from the actual code.

**Where each kind of function lives:**

- `extract_*()`                   → `R/data_sheets.R`
- `compute_data_sec_agg()`        → `R/compute_data_sec_agg.R`
- `compute_pareto_*()`, `compute_fig8_laffer()` → `R/compute_pareto.R`
- `compute_tab5()`                → `R/compute_tab5.R`
- `compute_billionaires_ca_inctax()` → `R/compute_billionaires_ca_inctax.R`
- `compute_shortrunseries()`      → `R/compute_shortrunseries.R`
- `compute_top4taxes()`           → `R/compute_top4taxes.R`
- `build_tab*_gt()`               → `R/tables.R`
- `build_fig*()`                  → `R/figures.R`

Each entry's header below repeats the file path, and the last line of each
listing gives the precise line range pulled from `getSrcref()`.

## `extract_data_dina()` {#sec-extract_data_dina}

```{r src-extract_data_dina, eval=FALSE, echo=TRUE, code=deparse_function("extract_data_dina")}
```

## `extract_data_sec_top4()` {#sec-extract_data_sec_top4}

```{r src-extract_data_sec_top4, eval=FALSE, echo=TRUE, code=deparse_function("extract_data_sec_top4")}
```

## `extract_longrunseries()` {#sec-extract_longrunseries}

```{r src-extract_longrunseries, eval=FALSE, echo=TRUE, code=deparse_function("extract_longrunseries")}
```

## `extract_shortrunseries()` {#sec-extract_shortrunseries}

```{r src-extract_shortrunseries, eval=FALSE, echo=TRUE, code=deparse_function("extract_shortrunseries")}
```

## `extract_tab2()` {#sec-extract_tab2}

```{r src-extract_tab2, eval=FALSE, echo=TRUE, code=deparse_function("extract_tab2")}
```

## `extract_tab3()` {#sec-extract_tab3}

```{r src-extract_tab3, eval=FALSE, echo=TRUE, code=deparse_function("extract_tab3")}
```

## `compute_billionaires_ca_inctax()` {#sec-compute_billionaires_ca_inctax}

```{r src-compute_billionaires_ca_inctax, eval=FALSE, echo=TRUE, code=deparse_function("compute_billionaires_ca_inctax")}
```

## `compute_data_sec_agg()` {#sec-compute_data_sec_agg}

```{r src-compute_data_sec_agg, eval=FALSE, echo=TRUE, code=deparse_function("compute_data_sec_agg")}
```

## `compute_fig8_laffer()` {#sec-compute_fig8_laffer}

```{r src-compute_fig8_laffer, eval=FALSE, echo=TRUE, code=deparse_function("compute_fig8_laffer")}
```

## `compute_pareto_missing()` {#sec-compute_pareto_missing}

```{r src-compute_pareto_missing, eval=FALSE, echo=TRUE, code=deparse_function("compute_pareto_missing")}
```

## `compute_shortrunseries()` {#sec-compute_shortrunseries}

```{r src-compute_shortrunseries, eval=FALSE, echo=TRUE, code=deparse_function("compute_shortrunseries")}
```

## `compute_tab5()` {#sec-compute_tab5}

```{r src-compute_tab5, eval=FALSE, echo=TRUE, code=deparse_function("compute_tab5")}
```

## `compute_top4taxes()` {#sec-compute_top4taxes}

```{r src-compute_top4taxes, eval=FALSE, echo=TRUE, code=deparse_function("compute_top4taxes")}
```

## `build_tab1()` {#sec-build_tab1}

```{r src-build_tab1, eval=FALSE, echo=TRUE, code=deparse_function("build_tab1")}
```

## `build_tab2()` {#sec-build_tab2}

```{r src-build_tab2, eval=FALSE, echo=TRUE, code=deparse_function("build_tab2")}
```

## `build_tab3()` {#sec-build_tab3}

```{r src-build_tab3, eval=FALSE, echo=TRUE, code=deparse_function("build_tab3")}
```

## `build_tab4()` {#sec-build_tab4}

```{r src-build_tab4, eval=FALSE, echo=TRUE, code=deparse_function("build_tab4")}
```

## `build_tab5()` {#sec-build_tab5}

```{r src-build_tab5, eval=FALSE, echo=TRUE, code=deparse_function("build_tab5")}
```

## `build_tab_a1()` {#sec-build_tab_a1}

```{r src-build_tab_a1, eval=FALSE, echo=TRUE, code=deparse_function("build_tab_a1")}
```

## `build_fig1()` {#sec-build_fig1}

```{r src-build_fig1, eval=FALSE, echo=TRUE, code=deparse_function("build_fig1")}
```

## `build_fig2()` {#sec-build_fig2}

```{r src-build_fig2, eval=FALSE, echo=TRUE, code=deparse_function("build_fig2")}
```

## `build_fig3()` {#sec-build_fig3}

```{r src-build_fig3, eval=FALSE, echo=TRUE, code=deparse_function("build_fig3")}
```

## `build_fig4()` {#sec-build_fig4}

```{r src-build_fig4, eval=FALSE, echo=TRUE, code=deparse_function("build_fig4")}
```

## `build_fig5()` {#sec-build_fig5}

```{r src-build_fig5, eval=FALSE, echo=TRUE, code=deparse_function("build_fig5")}
```

## `build_fig6()` {#sec-build_fig6}

```{r src-build_fig6, eval=FALSE, echo=TRUE, code=deparse_function("build_fig6")}
```

## `build_fig7()` {#sec-build_fig7}

```{r src-build_fig7, eval=FALSE, echo=TRUE, code=deparse_function("build_fig7")}
```

## `build_fig8()` {#sec-build_fig8}

```{r src-build_fig8, eval=FALSE, echo=TRUE, code=deparse_function("build_fig8")}
```

## `build_fig_a1()` {#sec-build_fig_a1}

```{r src-build_fig_a1, eval=FALSE, echo=TRUE, code=deparse_function("build_fig_a1")}
```

## `build_fig_a2()` {#sec-build_fig_a2}

```{r src-build_fig_a2, eval=FALSE, echo=TRUE, code=deparse_function("build_fig_a2")}
```

## `build_fig_a3()` {#sec-build_fig_a3}

```{r src-build_fig_a3, eval=FALSE, echo=TRUE, code=deparse_function("build_fig_a3")}
```

## `build_fig_a4()` {#sec-build_fig_a4}

```{r src-build_fig_a4, eval=FALSE, echo=TRUE, code=deparse_function("build_fig_a4")}
```

# Reproducibility

This report is built from the `{targets}` pipeline in the project root.
All upstream inputs come from `original-materials/BSZ_MainTablesFigures.xlsx`.
To re-render:

```r
targets::tar_make()
quarto::quarto_render("report.qmd")
```

The 506-expectation `testthat` suite (`Rscript tests/testthat.R`) verifies
every R re-derivation against the Excel cached values within documented
tolerances.
